---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Holland Sun"
date: "2026 Feb"
output: github_document
---


## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  

```{r load-data, message = FALSE, eval = FALSE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```
## Exercise 1-4

Foe example, If I click the link, the URL is:

``` https://collections.ed.ac.uk/art/record/99422?highlight=*:*```

What we scraped is:
```./record/99422?highlight=*:*"```

we need to replace the ```.``` with ``` https://collections.ed.ac.uk```

All other changes are saved in ```01-scrap-page-one.R```

## Exercise 5 & 6
See ```02-scrap-page-function.R```
```{r}
source("scripts/02-scrape-page-function.R")
first_url <- "https://collections.ed.ac.uk/art/search/*:*/Collection:%22edinburgh+college+of+art%7C%7C%7CEdinburgh+College+of+Art%22?offset=0"
scrape_page(first_url)

second_url <- "https://collections.ed.ac.uk/art/search/*:*/Collection:%22edinburgh+college+of+art%7C%7C%7CEdinburgh+College+of+Art%22?offset=10"
scrape_page(second_url)
```

## Exercise 7 8 9

See ```03-scrap-page-many.R```

## Exercise 10

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- read_csv("data/uoe-art.csv")
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)  # 
```
When running the code, 3 warnings are produced. 

The first warning tells us that 58 rows had more than one ```(``` in the title, so separate() only split at the first ```( ```and discarded the extra pieces. 

The second warning tells us that 599 rows had no ( at all, so the date column was filled with NA. 

The third warning tells us that some values in the date column could not be converted to numbers, so ```as.numeric()``` coerced them to NA. 

We are ok with these warnings because our goal is simply to capture year information where it is conveniently available. Entries that don't have a clean year in parentheses will just have NA for the year. 

## Exercise 11 

```{r}
skim(uoe_art)
```

Based on the `skim()` output, ```r sum(is.na(uoe_art$artist))``` pieces have missing artist information and ```r sum(is.na(uoe_art$year))``` pieces have missing year information.

## Exercise 12  

```{r}
ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 10)
```

There seems to be some(or one) outliers near 0，We can use arrange to double check
```{r}
uoe_art %>%
  filter(!is.na(year)) %>%
  arrange(year) %>%
  head(5)
```

It turned out that there was only one outlier. in year 2.


## Exercise 13  
The outlier piece is "Death Mask (2) (1964)". The correct year is 1964. Our code failed to capture the correct year because the title contains two sets of parentheses: "Death Mask (2) (1964)". Since separate() splits at the first (, it captured "2)" instead of "1964)", so it lead to  year of 2 .
```{r}
uoe_art <- uoe_art %>%
  mutate(year = if_else(year == 2, 1964, year))
ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 10)
```

It looks normal now.
## Exercise 14  
```{r}
uoe_art %>%
  count(artist, sort = TRUE) %>%
  head()
```
The most frequently featured artist is **"Unknown"**, who must be an incredibly versatile figure. I've seen this master's name across multiple fields. The second most common is **"Emma Gillies"**, whom I was not familiar with, but after checking Wikipedia, I found that she was a Scottish ceramic artist who studied and worked at the Edinburgh College of Art, so it makes sense that the university has a large collection of her work. The third most featured artist, **"NA"** is likely a master of programming and data processing who also dabbles in art in their spare time and it is quite impressive as well. I've also come across this name in these field.

## Exercise 15 

```{r}
childc <- uoe_art %>%
  filter(str_detect(title, regex("child", ignore_case = TRUE))) 
```
 
The word “child” appears ```r nrow(childc)``` times in these titles.